%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeEducation}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
        \textbf{\small#5:} {\small#6} \\
}


\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingNoBulletListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Akhil Kasamsetty} \\ \vspace{1pt}
    \small 469-520-4565 $|$ \href{mailto:akhilkasams@gmail.com}{\underline{akhilkasams@gmail.com}} $|$ 
    \href{https://linkedin.com/in/akhil-kasamsetty}{\underline{linkedin.com/in/akhil-kasamsetty}} $|$
    \href{https://github.com/akhilk999}{\underline{github.com/akhilk999}}
\end{center}


%-----------EDUCATION-----------

\section{Education}
  \resumeSubHeadingListStart
    \resumeEducation
      {Texas A\&M University}{May 2028}
      {Bachelor of Science in Computer Science}{GPA: 4.00}
      {Relevant Coursework}{Engineering Lab I - Computation (Intro to Python), Experimental Physics and Engineering Lab II - Mechanics, Program Design and Concepts (Intro to C++)}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Webmaster/Robotics Engineer}{Aug. 2024 -- Present}
      {Aggie Robotics - VEXU Team WHOOP}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Designed 10+ autonomous routes to position the robot and pick up and place items during matches.}
        \resumeItem{Implemented robot routes using C++ and the PROS VEX library to integrate with a motion sensor, optical sensor, IMU gyroscope sensors, and through bore encoders for robot localization and game strategy.}
        \resumeItem{Designed and built processor mount and clamping mechanism hardware using Autodesk Fusion 360.}
        \resumeItem{Team Accomplishments: Excellence Award and Robot Skills Champion @ Texas VEXU Robotics Competition, Energy Award, \#2 Seed, and Top 8 Teams in Math Division @ 2025 VEX Robotics World Championship}
      \resumeItemListEnd
    \resumeSubheading
      {Lead Python Curriculum Officer}{Aug. 2023 -- May 2024}
      {AIFA - AI For All }{Plano, TX}
      \resumeItemListStart
        \resumeItem{Led a team of 6 officers to create educational slideshows teaching Python to students at various high schools.}
        \resumeItem{Hosted an AI-based hackathon with 150+ participants at the \emph{University of Texas at Dallas.}}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Vice President/ Team Captain}{May 2021 -- May 2024}
      {Plano West Robotics - FTC Teams 14523, 12977}{Plano, TX}
      \resumeItemListStart
        \resumeItem{Led a team of 10+ engineers to design robot architecture and components in Autodesk Fusion 360.}
        \resumeItem{Increased development speed by 40\% by implementing team meetings and adding a Kanban board to track tasks.}
        \resumeItem{Hosted 10+ workshops and scrimmages for 1500+ people to help promote STEM throughout the community.}
        \resumeItem{Team Accomplishments: Inspire Award 2nd @ F\&E Qualifier, Finalist Alliance @ Texas UIL State Championship.}
    \resumeItemListEnd

    \resumeSubheading
      {Webmaster/Computer Science Tutor}{Feb. 2023 -- Oct. 2023}
      {Bloom Institute}{Virtual}
      \resumeItemListStart
        \resumeItem{Managed the website of an organization that hosts free year-round virtual classes for 200+ students.}
        \resumeItem{Designed and restructured website using WordPress to improve the layout and user experience.}
        \resumeItem{Tutored 50+ students in Python for a weekly class over the summer.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{SecureSimple}}{Nov. 2024 -- Nov. 2024}
          \resumeItemListStart
            \resumeItem{Worked with a team of 4 to design an electronic security system with an alarm and activation system in Multisim.}
            \resumeItem{Won 2nd Place in the SEC Ignite Design Challenge Electrical Engineering category.}
            \resumeItem{Created project report and video presentation on electronic security systems and our proposed product.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Legal AI Assistant} $|$ \emph{\url{https://github.com/akhilk999/Legal-AI-Assistant_backend}}}{Jun. 2024 -- Aug. 2024}
          \resumeItemListStart
            \resumeItem{Developed data extractor for Indian legal case file PDFs using Python and OpenAI API.}
            \resumeItem{Designed and implemented 4+ complete app wireframes using Figma and Flutter.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{FooDono} $|$ \emph{\url{https://github.com/akhilk999/FooDono}}}{Aug. 2020 -- Dec. 2020}
          \resumeItemListStart
            \resumeItem{Developed a mobile app to connect food banks to their visitors using Flutter, Firebase, and the Google Maps API.}
            \resumeItem{Won Honorable Mention in the Congressional App Challenge TX District 3.}
            \resumeItem{Added support for food banks to post available time slots and visitors to sign up for them, reducing overcrowding.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, Dart, C++, C\#, SQL (Postgres), JavaScript, HTML,CSS} \\
     \textbf{Frameworks}{: Flutter, Next.js, Tailwind CSS, WordPress, Material-UI, Bootstrap} \\
     \textbf{Developer Tools}{: Git, AWS, Figma, Android Studio, VS Code, TeXLive} \\
     \textbf{Libraries}{: NumPy, Matplotlib, Pandas, React} \\
     %\textbf{Software}{: Fusion 360, Blender, Figma, DaVinci Resolve, Photoshop} \\
     %\textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
